Impact of Demographics and Skills of the Observer on Visual Statistical Inference

### 2012-09-07 sociology_paper.tex
ouline description added

%\documentclass{article}
\documentclass[10pt]{article}
\usepackage{times}
%\usepackage{natbib}
%\usepackage{multicol}
\RequirePackage{natbib}
\usepackage{amsmath, amssymb, fullpage, amsthm, array,,graphicx,asa}
%\usepackage[dvips]{graphics}

@@

%\usepackage{setspace, url}
%\doublespacing

@@

\subsection{Choice of Visual Test Statistic} Discuss the effective feature of visual test statistics \citep{heike:2012}. May present some results from \textit{Distance measure} of visual test statistics \citep{niladri:2012}.
\subsection{Question that Human Observer Faces} Discuss the importance of the question the observer needs to answer while evaluating the lineup.
\subsection{Observer Personality}
\subsection{Visual Perception of Human Eye} Discuss the results we have on eye tracking experiment \citep{zhao:2012}.
\subsection{Demographics of Observer}  Age, gender and location of the observer.
\subsection{Skills of Observer} Knowledge about statistical plot as well as education level.

@@

\subsection{Experiment Setup}
\subsection{Diversity of the Experimental Subjects}

@@

% latex table generated in R 2.15.0 by xtable 1.7-0 package
% Fri Sep  7 10:28:47 2012
\begin{table}[hbtp]
\caption{Fixed effect parameter estimates of mixed model. Note that attempt is not significant for experiment 2. The continuous covariate lineup difficulty was measured by the $p$-value of the actual plot in the lineup.}
\begin{center}
\begin{tabular}{llrrrrl}
  \hline
& Parameters & Estimate & Std..Error & z.value & P-value  & \\ 
  \hline
\multicolumn{2}{l}{\bf{Experiment 1} } &&&& &\\
&(Intercept) & -0.30 & 0.10 & -2.89 & 0.00 & ***\\ 
 & attempt & 0.08 & 0.02 & 4.21 & 0.00 & ***\\ 
 & lineup difficulty & -11.32 & 1.01 & -11.19 & 0.00 & ***\\ 
\multicolumn{2}{l}{\bf{Experiment 2} } &&&&& \\
 & (Intercept) & 2.36 & 0.15 & 16.09 & 0.00 & ***\\ 
 & attempt & 0.01 & 0.03 & 0.35 & 0.72 \\ 
 & lineup difficulty & -55.03 & 2.20 & -25.00 & 0.00 & ***\\ 
\multicolumn{2}{l}{\bf{Experiment 3} } &&&& \\
 & (Intercept) & 0.25 & 0.16 & 1.58 & 0.11 & .\\ 
 & attempt & 0.10 & 0.03 & 3.34 & 0.00 & ***\\ 
 & lineup difficulty & 3.00 & 0.56 & 5.36 & 0.00 & ***\\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:model_par}
\end{table}

>>>>

%\documentclass{article}
\documentclass[10pt]{article}
\usepackage{times}
%\usepackage{natbib}
%\usepackage{multicol}
\RequirePackage{natbib}
\usepackage{amsmath, amssymb, fullpage, amsthm, array,,graphicx,asa, url}
%\usepackage[dvips]{graphics}

@@

%\usepackage{setspace}
%\doublespacing

@@

\subsection{Choice of Visual Test Statistic} Discuss the effective feature of visual test statistics \citep{heike:2012}. Present some related results from \textit{Distance measure} of visual test statistics \citep{niladri:2012}.
\subsection{Question that Human Observer Faces} Discuss the importance of the question the observer needs to answer while evaluating the lineup.
\subsection{Observer Personality}
\subsection{Visual Perception of Human Eye} Discuss the results we have on eye tracking experiment \citep{zhao:2012}.
\subsection{Demographics of Observer}  Age, gender and location of the observer.
\subsection{Skills of Observer} Knowledge about statistical plot as well as education level.

@@

\subsection{Experiment Setup} Description of the simulation experiment giving focus on demographics and skills of experimental subjects.
\subsection{Diversity of the Experimental Subjects} Discuss why it would be important and how we accomplish this using Amazon Mechanical Turk \cite{turk} web site.

@@

% latex table generated in R 2.15.0 by xtable 1.7-0 package
% Fri Sep  7 10:28:47 2012
\begin{table}[hbtp]
\caption{Fixed effect parameter estimates of generalized mixed model. Note that attempt is not significant for experiment 2. The continuous covariate, lineup difficulty, was measured by the $p$-value of the actual plot in the lineup.}
\begin{center}
\begin{tabular}{llrrrrl}
  \hline
& Parameters & Estimate & Std..Error & z.value & P-value  & \\ 
  \hline
\multicolumn{2}{l}{\bf{Experiment 1} } &&&& &\\
&(Intercept) & -0.30 & 0.10 & -2.89 & 0.00 & ***\\ 
 & attempt & 0.08 & 0.02 & 4.21 & 0.00 & ***\\ 
 & lineup difficulty & -11.32 & 1.01 & -11.19 & 0.00 & ***\\ 
\multicolumn{2}{l}{\bf{Experiment 2} } &&&&& \\
 & (Intercept) & 2.36 & 0.15 & 16.09 & 0.00 & ***\\ 
 & attempt & 0.01 & 0.03 & 0.35 & 0.72 \\ 
 & lineup difficulty & -55.03 & 2.20 & -25.00 & 0.00 & ***\\ 
\multicolumn{2}{l}{\bf{Experiment 3} } &&&& \\
 & (Intercept) & 0.25 & 0.16 & 1.58 & 0.11 & .\\ 
 & attempt & 0.10 & 0.03 & 3.34 & 0.00 & ***\\ 
 & lineup difficulty & 3.00 & 0.56 & 5.36 & 0.00 & ***\\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:model_par}
\end{table}
